---
title: "MSc Study Wave 2 Wrangeling"
author: "Hanna L Glandorf"
date: "20 7 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MSc Study Data Clean-up Wave 2
The code here cleans up data that was downloaded from a survey on an online platform. The survey represents the second wave of data for this study.

Objectives are:
- correct column names in each data file
- combine data files from the five orders
- correct coding of each item
- check internal consistency of each questionnaire
- compute total scores for each questionnaire

# Load libraries and import data
```{r read-in}
library(broom)
library(tidyverse)
library(ggplot2)
library(psych) 


w2o1 <- readxl::read_excel("wave2order1.xlsx") %>%
  mutate(id = 1:23)
w2o2 <- readxl::read_excel("wave2order2.xlsx") %>%
  mutate(id = 24:34)
w2o3 <- readxl::read_excel("wave2order3.xlsx") %>%
  mutate(id = 35:51)
w2o4 <- readxl::read_excel("wave2order4.xlsx") %>%
  mutate(id = 52:68)
w2o5 <- readxl::read_excel("wave2order5.xlsx") %>%
  mutate(id = 69:95)
```

Order 1 (for reference):
- Q2_1-Q2_5 devaluation
- Q3_1-3_10 ABQ rest (exhaustion and reduced sense of accomplishment)
- Q4_1-4_10 PSS (stress)
- Q5_1-5_9 SIQS (team identification; three-dimensional)
- Q6_1-6_6 BPSSQ (perceived social support)
- Q7_1-7_4 FISI (team identification; one-dimensional)
- Q8 unique identifier
```{r selection}
w2o1_s <- w2o1 %>% select(id, Q2_1, Q2_2, Q2_3, Q2_4, Q2_5, Q3_1, Q3_2, Q3_3, Q3_4, Q3_5, Q3_6, Q3_7, Q3_8, Q3_9, Q3_10, Q4_1, Q4_2, Q4_3, Q4_4, Q4_5, Q4_6, Q4_7, Q4_8, Q4_9, Q4_10, Q5_1, Q5_2, Q5_3, Q5_4, Q5_5, Q5_6, Q5_7, Q5_8, Q5_9, Q6_1, Q6_2, Q6_3, Q6_4, Q6_5, Q6_6, Q7_1, Q7_2, Q7_3, Q7_4, Q8)

w2o1_s <- w2o1_s %>% rename(deval1w2 = Q2_1, #devaluation
                            deval2w2 = Q2_2,
                            deval3w2 = Q2_3,
                            deval4w2 = Q2_4,
                            deval5w2 = Q2_5,
                            exh1w2 = Q3_2, #exhaustion
                            exh2w2 = Q3_3,
                            exh3w2 = Q3_6,
                            exh4w2 = Q3_7,
                            exh5w2 = Q3_8,
                            accom1w2 = Q3_1, #reduced sense of accomplishment
                            accom2w2 = Q3_4,
                            accom3w2 = Q3_5,
                            accom4w2 = Q3_9,
                            accom5w2 = Q3_10,
                            pss1w2 = Q4_1, #perceived stress
                            pss2w2 = Q4_2,
                            pss3w2 = Q4_3,
                            pss4w2 = Q4_4,
                            pss5w2 = Q4_5,
                            pss6w2 = Q4_6,
                            pss7w2 = Q4_7,
                            pss8w2 = Q4_8,
                            pss9w2 = Q4_9,
                            pss10w2 = Q4_10,
                            fisi1w2 = Q7_1, #team identification
                            fisi2w2 = Q7_2,
                            fisi3w2 = Q7_3,
                            fisiw2 = Q7_4,
                            bpssq1w2 = Q6_1, #perceived social support
                            bpssq2w2 = Q6_2,
                            bpssq3w2 = Q6_3,
                            bpssq4w2 = Q6_4,
                            bpssq5w2 = Q6_5,
                            bpssq6w2 = Q6_6,
                            ties1w2 = Q5_1, #team identification (first dimension)
                            ties2w2 = Q5_2,
                            ties3w2 = Q5_3,
                            centr1w2 = Q5_4, #team identification (second dimension)
                            centr2w2 = Q5_5,
                            centr3w2 = Q5_6,
                            aff1w2 = Q5_7, #team identification (third dimension)
                            aff2w2 = Q5_8,
                            aff3w2 = Q5_9,
                            u_id = Q8)
```

Order 2 (for reference):
- Q2 = PSS
- Q3 = devaluation
- Q4 = exhaustion and red accomplishments
- Q5 = BPSSQ
- Q6 = SIQS
- Q7 = FISI
- Q8 = identifier
```{r}
w2o2_s <- w2o2 %>% select(id, Q2_1, Q2_2, Q2_3, Q2_4, Q2_5, Q2_6, Q2_7, Q2_8, Q2_9, Q2_10, Q3_1, Q3_2, Q3_3, Q3_4, Q3_5, Q4_1, Q4_2, Q4_3, Q4_4, Q4_5, Q4_6, Q4_7, Q4_8, Q4_9, Q4_10, Q5_1, Q5_2, Q5_3, Q5_4, Q5_5, Q5_6, Q6_1, Q6_2, Q6_3, Q6_4, Q6_5, Q6_6, Q6_7, Q6_8, Q6_9, Q7_1, Q7_2, Q7_3, Q7_4, Q8)

w2o2_s <- w2o2_s %>% rename(deval1w2 = Q3_1,
                            deval2w2 = Q3_2,
                            deval3w2 = Q3_3,
                            deval4w2 = Q3_4,
                            deval5w2 = Q3_5,
                            exh1w2 = Q4_2,
                            exh2w2 = Q4_3,
                            exh3w2 = Q4_6,
                            exh4w2 = Q4_7,
                            exh5w2 = Q4_8,
                            accom1w2 = Q4_1,
                            accom2w2 = Q4_4,
                            accom3w2 = Q4_5,
                            accom4w2 = Q4_9,
                            accom5w2 = Q4_10,
                            pss1w2 = Q2_1,
                            pss2w2 = Q2_2,
                            pss3w2 = Q2_3,
                            pss4w2 = Q2_4,
                            pss5w2 = Q2_5,
                            pss6w2 = Q2_6,
                            pss7w2 = Q2_7,
                            pss8w2 = Q2_8,
                            pss9w2 = Q2_9,
                            pss10w2 = Q2_10,
                            fisi1w2 = Q7_1,
                            fisi2w2 = Q7_2,
                            fisi3w2 = Q7_3,
                            fisi4w2 = Q7_4,
                            bpssq1w2 = Q5_1,
                            bpssq2w2 = Q5_2,
                            bpssq3w2 = Q5_3,
                            bpssq4w2 = Q5_4,
                            bpssq5w2 = Q5_5,
                            bpssq6w2 = Q5_6,
                            ties1w2 = Q6_1,
                            ties2w2 = Q6_2,
                            ties3w2 = Q6_3,
                            centr1w2 = Q6_4,
                            centr2w2 = Q6_5,
                            centr3w2 = Q6_6,
                            aff1w2 = Q6_7,
                            aff2w2 = Q6_8,
                            aff3w2 = Q6_9,
                            u_id = Q8)
```

Order 3 (for reference):
- Q2 = SIQS
- Q3 = BPSSQ
- Q4 = devaluation
- Q5 = red accomplishments and exhaustion
- Q6 = FISI
- Q7 = PSS
- Q8 = unique identifier
```{r}
w2o3_s <- w2o3 %>% select(id, Q2_1, Q2_2, Q2_3, Q2_4, Q2_5, Q2_6, Q2_7, Q2_8, Q2_9, Q3_1, Q3_2, Q3_3, Q3_4, Q3_5, Q3_6, Q4_1, Q4_2, Q4_3, Q4_4, Q4_5, Q5_1, Q5_2, Q5_3, Q5_4, Q5_5, Q5_6, Q5_7, Q5_8, Q5_9, Q5_10, Q6_1, Q6_2, Q6_3, Q6_4, Q7_1, Q7_2, Q7_3, Q7_4, Q7_5, Q7_6, Q7_7, Q7_8, Q7_9, Q7_10, Q8)

w2o3_s <- w2o3_s %>% rename(deval1w2 = Q4_1,
                            deval2w2 = Q4_2,
                            deval3w2 = Q4_3,
                            deval4w2 = Q4_4,
                            deval5w2 = Q4_5,
                            exh1w2 = Q5_2,
                            exh2w2 = Q5_3,
                            exh3w2 = Q5_6,
                            exh4w2 = Q5_7,
                            exh5w2 = Q5_8,
                            accom1w2 = Q5_1,
                            accom2w2 = Q5_4,
                            accom3w2 = Q5_5,
                            accom4w2 = Q5_9,
                            accom5w2 = Q5_10,
                            pss1w2 = Q7_1,
                            pss2w2 = Q7_2,
                            pss3w2 = Q7_3,
                            pss4w2 = Q7_4,
                            pss5w2 = Q7_5,
                            pss6w2 = Q7_6,
                            pss7w2 = Q7_7,
                            pss8w2 = Q7_8,
                            pss9w2 = Q7_9,
                            pss10w2 = Q7_10,
                            fisi1w2 = Q6_1,
                            fisi2w2 = Q6_2,
                            fisi3w2 = Q6_3,
                            fisi4w2 = Q6_4,
                            bpssq1w2 = Q3_1,
                            bpssq2w2 = Q3_2,
                            bpssq3w2 = Q3_3,
                            bpssq4w2 = Q3_4,
                            bpssq5w2 = Q3_5,
                            bpssq6w2 = Q3_6,
                            ties1w2 = Q2_1,
                            ties2w2 = Q2_2,
                            ties3w2 = Q2_3,
                            centr1w2 = Q2_4,
                            centr2w2 = Q2_5,
                            centr3w2 = Q2_6,
                            aff1w2 = Q2_7,
                            aff2w2 = Q2_8,
                            aff3w2 = Q2_9,
                            u_id = Q8)
```

Order 4 (for reference):
- Q2 = BPSSQ
- Q3 = PSS
- Q4 = FISI
- Q5 = devaluation
- Q6 = accom and exhaustion
- Q7 = SIQS (missing item 4)
- Q8 = identifier
```{r}
w2o4_s <- w2o4 %>% select(id, Q2_1, Q2_2, Q2_3, Q2_4, Q2_5, Q2_6, Q3_1, Q3_2, Q3_3, Q3_4, Q3_5, Q3_6, Q3_7, Q3_8, Q3_9, Q3_10, Q4_1, Q4_2, Q4_3, Q4_4, Q5_1, Q5_2, Q5_3, Q5_4, Q5_5, Q6_1, Q6_2, Q6_3, Q6_4, Q6_5, Q6_6, Q6_7, Q6_8, Q6_8, Q6_9, Q6_10, Q7_1, Q7_2, Q7_3, Q7_4, Q7_5, Q7_6, Q7_7, Q7_8, Q7_9, Q8)

w2o4_s <- w2o4_s %>% rename(deval1w2 = Q5_1,
                            deval2w2 = Q5_2,
                            deval3w2 = Q5_3,
                            deval4w2 = Q5_4,
                            deval5w2 = Q5_5,
                            exh1w2 = Q6_2,
                            exh2w2 = Q6_3,
                            exh3w2 = Q6_6,
                            exh4w2 = Q6_7,
                            exh5w2 = Q6_8,
                            accom1w2 = Q6_1,
                            accom2w2 = Q6_4,
                            accom3w2 = Q6_5,
                            accom4w2 = Q6_9,
                            accom5w2 = Q6_10,
                            pss1w2 = Q3_1,
                            pss2w2 = Q3_2,
                            pss3w2 = Q3_3,
                            pss4w2 = Q3_4,
                            pss5w2 = Q3_5,
                            pss6w2 = Q3_6,
                            pss7w2 = Q3_7,
                            pss8w2 = Q3_8,
                            pss9w2 = Q3_9,
                            pss10w2 = Q3_10,
                            fisi1w2 = Q4_1,
                            fisi2w2 = Q4_2,
                            fisi3w2 = Q4_3,
                            fisi4w2 = Q4_4,
                            bpssq1w2 = Q2_1,
                            bpssq2w2 = Q2_2,
                            bpssq3w2 = Q2_3,
                            bpssq4w2 = Q2_4,
                            bpssq5w2 = Q2_5,
                            bpssq6w2 = Q2_6,
                            ties1w2 = Q7_1,
                            ties2w2 = Q7_2,
                            ties3w2 = Q7_3,
                            centr1w2 = Q7_4,
                            centr2w2 = Q7_5,
                            centr3w2 = Q7_6,
                            aff1w2 = Q7_7,
                            aff2w2 = Q7_8,
                            aff3w2 = Q7_9,
                            u_id = Q8)
```

Order 5 (for reference):
- Q2 = FISI
- Q3 = BPSSQ
- Q4 = PSS
- Q5 = SIQS
- Q6 = devaluation
- Q7 = red accomplishment and exhaustion
- Q8 = unique identifier
```{r}
w2o5_s <- w2o5 %>% select(id, Q2_1, Q2_2, Q2_3, Q2_4, Q3_1, Q3_2, Q3_3, Q3_4, Q3_5, Q3_6, Q4_1, Q4_2, Q4_3, Q4_4, Q4_5, Q4_6, Q4_7, Q4_8, Q4_9, Q4_10, Q5_1, Q5_2, Q5_3, Q5_4, Q5_5, Q5_6, Q5_7, Q5_8, Q5_9, Q6_1, Q6_2, Q6_3, Q6_4, Q6_5, Q7_1, Q7_2, Q7_3, Q7_4, Q7_5, Q7_6, Q7_7, Q7_8, Q7_9, Q7_10, Q8)

w2o5_s <- w2o5_s %>% rename(deval1w2 = Q6_1,
                            deval2w2 = Q6_2,
                            deval3w2 = Q6_3,
                            deval4w2 = Q6_4,
                            deval5w2 = Q6_5,
                            exh1w2 = Q7_2,
                            exh2w2 = Q7_3,
                            exh3w2 = Q7_6,
                            exh4w2 = Q7_7,
                            exh5w2 = Q7_8,
                            accom1w2 = Q7_1,
                            accom2w2 = Q7_4,
                            accom3w2 = Q7_5,
                            accom4w2 = Q7_9,
                            accom5w2 = Q7_10,
                            pss1w2 = Q4_1,
                            pss2w2 = Q4_2,
                            pss3w2 = Q4_3,
                            pss4w2 = Q4_4,
                            pss5w2 = Q4_5,
                            pss6w2 = Q4_6,
                            pss7w2 = Q4_7,
                            pss8w2 = Q4_8,
                            pss9w2 = Q4_9,
                            pss10w2 = Q4_10,
                            fisi1w2 = Q2_1,
                            fisi2w2 = Q2_2,
                            fisi3w2 = Q2_3,
                            fisi4w2 = Q2_4,
                            bpssq1w2 = Q3_1,
                            bpssq2w2 = Q3_2,
                            bpssq3w2 = Q3_3,
                            bpssq4w2 = Q3_4,
                            bpssq5w2 = Q3_5,
                            bpssq6w2 = Q3_6,
                            ties1w2 = Q5_1,
                            ties2w2 = Q5_2,
                            ties3w2 = Q5_3,
                            centr1w2 = Q5_4,
                            centr2w2 = Q5_5,
                            centr3w2 = Q5_6,
                            aff1w2 = Q5_7,
                            aff2w2 = Q5_8,
                            aff3w2 = Q5_9,
                            u_id = Q8)
```

# Correct coding of items (e.g., reverse coding)
```{r}
datcomb2 <- bind_rows(w2o1_s, w2o2_s, w2o3_s, w2o4_s, w2o5_s)
## correct coding
datcomb2 <- datcomb2 %>% mutate(deval1w2 = recode(deval1w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                deval2w2 = recode(deval2w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                deval3w2 = recode(deval3w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                deval4w2 = recode(deval4w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                deval5w2 = recode(deval5w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                exh1w2 = recode(exh1w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                exh2w2 = recode(exh2w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                exh3w2 = recode(exh3w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                exh4w2 = recode(exh4w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                exh5w2 = recode(exh5w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                accom1w2 = recode(accom1w2, "6" = "NA", "5"="0", "4"="1", "3"="2", "2"="3", "1"="4"),
                accom2w2 = recode(accom2w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                accom3w2 = recode(accom3w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                accom4w2 = recode(accom4w2, "6" = "NA", "5"="4", "4"="3", "3"="2", "2"="1", "1"="0"),
                accom5w2 = recode(accom5w2, "6" = "NA", "5"="0", "4"="1", "3"="2", "2"="3", "1"="4"),
                pss1w2 = recode(pss1w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                pss2w2 = recode(pss2w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                pss3w2 = recode(pss3w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                pss4w2 = recode(pss4w2, "1"=4, "2"=3, "3"=2, "4"=1, "5"=0),
                pss5w2 = recode(pss5w2, "1"=4, "2"=3, "3"=2, "4"=1, "5"=0),
                pss6w2 = recode(pss6w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                pss7w2 = recode(pss7w2, "1"=4, "2"=3, "3"=2, "4"=1, "5"=0),
                pss8w2 = recode(pss8w2, "1"=4, "2"=3, "3"=2, "4"=1, "5"=0),
                pss9w2 = recode(pss9w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4),
                pss10w2 = recode(pss10w2, "1"=0, "2"=1, "3"=2, "4"=3, "5"=4))
##convert to numeric
datcomb2$exh1w2 <- as.numeric(as.character(datcomb2$exh1w2))
datcomb2$exh2w2 <- as.numeric(as.character(datcomb2$exh2w2))
datcomb2$exh3w2 <- as.numeric(as.character(datcomb2$exh3w2))
datcomb2$exh4w2 <- as.numeric(as.character(datcomb2$exh4w2))
datcomb2$exh5w2 <- as.numeric(as.character(datcomb2$exh5w2))

datcomb2$accom1w2 <- as.numeric(as.character(datcomb2$accom1w2))
datcomb2$accom2w2 <- as.numeric(as.character(datcomb2$accom2w2))
datcomb2$accom3w2 <- as.numeric(as.character(datcomb2$accom3w2))
datcomb2$accom4w2 <- as.numeric(as.character(datcomb2$accom4w2))
datcomb2$accom5w2 <- as.numeric(as.character(datcomb2$accom5w2))

datcomb2$ties1w2 <- as.numeric(as.character(datcomb2$ties1w2))
datcomb2$ties2w2 <- as.numeric(as.character(datcomb2$ties2w2))
datcomb2$ties3w2 <- as.numeric(as.character(datcomb2$ties3w2))

datcomb2$centr1w2 <- as.numeric(as.character(datcomb2$centr1w2))
datcomb2$centr2w2 <- as.numeric(as.character(datcomb2$centr2w2))
datcomb2$centr3w2 <- as.numeric(as.character(datcomb2$centr3w2))

datcomb2$aff1w2 <- as.numeric(as.character(datcomb2$aff1w2))
datcomb2$aff2w2 <- as.numeric(as.character(datcomb2$aff2w2))
datcomb2$aff3w2 <- as.numeric(as.character(datcomb2$aff3w2))

datcomb2$bpssq1w2 <- as.numeric(as.character(datcomb2$bpssq1w2))
datcomb2$bpssq2w2 <- as.numeric(as.character(datcomb2$bpssq2w2))
datcomb2$bpssq3w2 <- as.numeric(as.character(datcomb2$bpssq3w2))
datcomb2$bpssq4w2 <- as.numeric(as.character(datcomb2$bpssq4w2))
datcomb2$bpssq5w2 <- as.numeric(as.character(datcomb2$bpssq5w2))
datcomb2$bpssq6w2 <- as.numeric(as.character(datcomb2$bpssq6w2))

datcomb2$fisi1w2 <- as.numeric(as.character(datcomb2$fisi1w2))
datcomb2$fisi2w2 <- as.numeric(as.character(datcomb2$fisi2w2))
datcomb2$fisi3w2 <- as.numeric(as.character(datcomb2$fisi3w2))
datcomb2$fisi4w2 <- as.numeric(as.character(datcomb2$fisi4w2))
```

# Check for internal consistency
Check internal consistency with Cronbach's alpha.
```{r}
##pss
pss_alpha <- datcomb2 %>% dplyr::select(pss1w2, pss2w2, pss3w2, pss4w2, pss5w2, pss6w2, pss7w2, pss8w2, pss9w2, pss10w2)
alpha(pss_alpha[,1:10], check.keys = F)

##abq
deval_alpha <- datcomb2 %>% dplyr::select(deval1w2, deval2w2, deval3w2, deval4w2, deval5w2)
alpha(deval_alpha[,1:5], check.keys = F)

exh_alpha <- datcomb2 %>% dplyr::select(exh1w2, exh2w2, exh3w2, exh4w2, exh5w2)
alpha(exh_alpha[,1:5], check.keys = F)

accom_alpha <- datcomb2 %>% dplyr::select(accom1w2, accom2w2, accom3w2, accom4w2, accom5w2)
alpha(accom_alpha[,1:5], check.keys = T) ##item 1 and 5 negatively correlated with scale, covid context?

##fisi
fisi_alpha <- datcomb2 %>% dplyr::select(fisi1w2, fisi2w2, fisi3w2, fisi4w2)
alpha(fisi_alpha[,1:4], check.keys = F)

##bpssq
bpssq_alpha <- datcomb2 %>% dplyr::select(bpssq1w2, bpssq2w2, bpssq3w2, bpssq4w2, bpssq5w2, bpssq6w2)
alpha(bpssq_alpha[,1:6], check.keys = F)

##ssiq
ties_alpha <- datcomb2 %>% dplyr::select(ties1w2, ties2w2, ties3w2)
alpha(ties_alpha[,1:3], check.keys = F)

centr_alpha <- datcomb2 %>% dplyr::select(centr1w2, centr2w2, centr3w2)
alpha(centr_alpha[,1:3], check.keys = F)

aff_alpha <- datcomb2 %>% dplyr::select(aff1w2, aff2w2, aff3w2)
alpha(aff_alpha[,1:3], check.keys = F)

#apart from reduced sense of accomplishment, all other scales meet alpha = 0.7
```

# Check use of burnout items
Checking whether participants completed the exhaustion and reduced sense of accomplishment items. This was done, because we were unsure how relevant these items would be in the COVID-19 context.
```{r}
datcomb2 %>% group_by(exh1w2) %>% summarise(n())
datcomb2 %>% group_by(exh2w2) %>% summarise(n())
datcomb2 %>% group_by(exh3w2) %>% summarise(n())
datcomb2 %>% group_by(exh4w2) %>% summarise(n())
datcomb2 %>% group_by(exh5w2) %>% summarise(n())

datcomb2 %>% group_by(accom1w2) %>% summarise(n())
datcomb2 %>% group_by(accom2w2) %>% summarise(n())
datcomb2 %>% group_by(accom3w2) %>% summarise(n())
datcomb2 %>% group_by(accom4w2) %>% summarise(n())
datcomb2 %>% group_by(accom5w2) %>% summarise(n())
```

# Compute total scores for each questionnaire
```{r}

datcomb2_c <- mutate(datcomb2, t2pss = pss1w2+pss2w2+pss3w2+pss4w2+pss5w2+pss6w2+pss7w2+pss8w2+pss9w2+pss10w2,
                     t2pssf1 = pss1w2+pss2w2+pss3w2+pss6w2+pss9w2+pss10w2,
                     t2pssf2 = pss4w2+pss5w2+pss7w2+pss8w2,
               t2fisi = fisi1w2+fisi2w2+fisi3w2+fisi4w2,
               t2deval = (deval1w2+deval2w2+deval3w2+deval4w2+deval5w2)/5,
               t2exh = (exh1w2+exh2w2+exh3w2+exh4w2+exh5w2)/5,
               t2accom = (accom1w2+accom2w2+accom3w2+accom4w2+accom5w2)/5, ##item 1 and 5 were removed to achieve alpha of 0.86
               t2ties = (ties1w2+ties2w2+ties3w2)/3,
               t2centr = (centr1w2+centr2w2+centr3w2)/3,
               t2aff = (aff1w2+aff2w2+aff3w2)/3,
               t2bpssq = bpssq1w2+bpssq2w2+bpssq3w2+bpssq4w2+bpssq5w2+bpssq6w2)

```

# Create cleaned data file
```{r}
write.csv(datcomb2_c, file = 'wave2.csv')
```
